Graph Topological Aspects of Granger Causal Network Learning

### 2019-07-10 paper/paper.tex
typo.

For later use, and to get a feel for the topological implications of
strong causality We explore a number of properties of such graphs
before moving into the main result of this section.  The following
important property essentially strengthens proposition
\ref{prop:ancestor_properties} for the case of strongly causal graphs.

>>>>

For later use, and to get a feel for the topological implications of
strong causality, we explore a number of properties of such graphs
before moving into the main result of this section.  The following
important property essentially strengthens proposition
\ref{prop:ancestor_properties} for the case of strongly causal graphs.
